Provenance analysis

### 2021-08-06 analysis/provenance2.Rmd
Provenance classification

>>>>

# Classification

```{r classification_calls}

string_calls <- E_prov %>% filter(provenance %in% c("parse", "str2lang", "str2expression"))

reflection_calls <- E_prov %>% filter(provenance %in% c("match.call", "formals", "substitute") | (provenance == "quote" & type != "symbol"))

constructed_calls <- E_prov %>% filter(provenance %in% c("expression", "quote", "enquote", "call", "as.call", "as.vector"))

symbol_calls <- E_prov %>% filter(provenance %in% c("as.name", "as.symbol") | (provenance == "quote" & type == "symbol"))

```{r classification_sites}

string_sites <- string_calls %>% pull(src_ref) %>% n_distinct()

reflection_sites <- reflection_calls %>% pull(src_ref) %>% n_distinct()

constructed_sites <- constructed_calls %>%  pull(src_ref) %>% n_distinct()

symbol_sites <- symbol_calls %>% pull(src_ref) %>% n_distinct()

r("nb string sites", string_sites)
r("string sites percent", ratio(string_sites, nb_call_sites))

r("nb reflection sites", reflection_sites)
r("reflection sites percent", ratio(reflection_sites, nb_call_sites))

r("nb constructed sites", constructed_sites)
r("constructed sites percent", ratio(constructed_sites, nb_call_sites))

r("nb symbol sites", symbol_sites)
r("symbol sites percent", ratio(symbol_sites, nb_call_sites))
